Navigating to a greener Europe with 24/7 hourly carbon-free electricity procurement

### 2023-10-15 manuscript/manuscript.tex
manuscript: add acknowledgements

This paper is an independent project, which is based on the third-party funded research work \cite{riepin-zenodo-systemlevel247}.
This research work was supported by a grant from Google Inc.

>>>>

This work is an independent follow-up to the prior public report by the authors \cite{riepin-zenodo-systemlevel247} with an updated model, updated system-wide assumptions, and additional analysis of the results. The prior public report was supported by a research grant from Google LLC.

We thank the following people for fruitful discussions on the 24/7 carbon-free energy procurement and the art of energy system modelling: Fabian Neumann, Elisabeth Zeyen, Devon Swezey.
